Evaluation of Diagnostic Concordance Between Algorithms for Parkinson’s Disease Dementia

### 2025-10-10 _manuscript/manuscript.qmd
Documentation updated.

data <- tar_read(raw_data, store = upstore)
crit <- tar_read(pdd_data, store = upstore)$criteria
vars <- tar_read(variables, store = upstore)
```

@@

continue <- !any(critnum == 0)
stopifnot("Some criteria are missing" = continue)
```

@@

table_criteria(vars)
```

>>>>

data <- tar_read(raw_data, store = upstore)
crit <- tar_read(pdd_data, store = upstore)$algorithms
vars <- tar_read(variables, store = upstore)
```

@@

continue <- !any(critnum == 0)
stopifnot("Some algorithms are missing" = continue)
```

@@

table_algorithms(vars)
```
